---
title: "Content Review"
format:
  html:
    toc: false
execute:
  echo: false
  warning: false
  message: false
  freeze: true
---

```{r setup, include=FALSE}
items <- read.csv("data/item_quality_template.csv", stringsAsFactors = FALSE, encoding = "UTF-8")
items <- items[, c("quest", "quest_label", "domain", "item_code", "item_text_ar", "item_text_en")]
items <- items[!is.na(items$item_code) & nchar(trimws(items$item_code)) > 0, ]
items <- items[order(items$quest, items$domain, items$item_code), ]
n_items <- nrow(items)
```

```{css}
:root {
  --primary-green: #1DB584;
  --secondary-blue: #4A90E2;
  --light-gray: #F5F5F5;
  --dark-text: #333333;
  --border-gray: #CCCCCC;
}

* { margin: 0; padding: 0; box-sizing: border-box; }

html, body {
  font-family: -apple-system, BlinkMacSystemFont, 'Segoe UI', Roboto, Helvetica, Arial, sans-serif;
  background-color: var(--light-gray);
  color: var(--dark-text);
  line-height: 1.6;
}

.hero-section {
  background: linear-gradient(135deg, var(--primary-green) 0%, var(--secondary-blue) 100%);
  color: white;
  padding: 60px 40px;
  text-align: center;
  margin-bottom: 50px;
}
.hero-section h1 { font-size: 2.5em; margin-bottom: 20px; font-weight: 700; }
.hero-section p { font-size: 1.1em; max-width: 800px; margin: 0 auto; line-height: 1.8; opacity: 0.98; }

.message-box {
  padding: 15px 20px; margin-bottom: 30px; border-radius: 4px;
  border-left: 5px solid var(--primary-green); background-color: #EAFAF3;
  color: #1a6643; display: none;
}
.message-box.success { display: block; }
.message-box.error { border-left-color: #DC3545; background-color: #F8D7DA; color: #721C24; display: block; }

.section-box {
  background: white; margin-bottom: 40px; border-radius: 6px;
  box-shadow: 0 2px 8px rgba(0,0,0,0.1); padding: 40px;
}
.section-title {
  font-size: 1.8em; font-weight: 700; color: var(--primary-green);
  margin-bottom: 10px; padding-bottom: 15px; border-bottom: 3px solid var(--secondary-blue);
}
.section-description {
  color: #666; font-size: 0.95em; margin-bottom: 30px; padding: 15px;
  background-color: var(--light-gray); border-radius: 4px; border-left: 4px solid var(--secondary-blue);
}

.form-grid { display: grid; grid-template-columns: 1fr 1fr; gap: 25px; margin-bottom: 30px; }
.form-grid.full { grid-template-columns: 1fr; }
.form-group { display: flex; flex-direction: column; }
.form-group label { font-weight: 600; margin-bottom: 8px; font-size: 0.95em; color: var(--dark-text); }
.form-group label .required { color: #DC3545; margin-left: 3px; }
.form-group input, .form-group select, .form-group textarea {
  padding: 12px 14px; border: 2px solid var(--border-gray); border-radius: 4px;
  font-size: 1em; font-family: inherit; background-color: white; color: var(--dark-text);
}
.form-group textarea { resize: vertical; min-height: 80px; }

.table-wrapper { overflow-x: auto; margin-top: 30px; }
.item-table { width: 100%; border-collapse: collapse; font-size: 0.95em; }
.item-table thead { background-color: var(--primary-green); color: white; position: sticky; top: 0; z-index: 10; }
.item-table thead th { padding: 15px 12px; text-align: left; font-weight: 600; border: 1px solid #999; }
.item-table tbody tr { border-bottom: 1px solid #ddd; }
.item-table tbody tr:nth-child(even) { background-color: #FAFAFA; }
.item-table td { padding: 12px; border: 1px solid #ddd; }
.rating-select { width: 70px; padding: 8px; border: 1px solid var(--border-gray); border-radius: 3px; font-size: 0.9em; }
.comment-textarea {
  width: 100%; padding: 8px; border: 1px solid var(--border-gray); border-radius: 3px;
  font-size: 0.85em; min-height: 60px; font-family: inherit; resize: vertical;
}

.button-container { display: flex; gap: 15px; justify-content: center; margin-top: 50px; flex-wrap: wrap; }
.btn {
  padding: 14px 40px; border: none; border-radius: 4px; font-size: 1em;
  font-weight: 600; cursor: pointer; text-transform: uppercase; letter-spacing: 0.5px;
}
.btn-primary { background-color: var(--primary-green); color: white; }
.btn-primary:hover { background-color: #169D6E; }
.btn-secondary { background-color: var(--secondary-blue); color: white; }
.btn-secondary:hover { background-color: #3A7BC8; }
.btn-download { background-color: #6c757d; color: white; }
.btn-download:hover { background-color: #545b62; }

@media (max-width: 768px) {
  .form-grid { grid-template-columns: 1fr; }
  .section-box { padding: 20px; }
  .hero-section { padding: 40px 20px; }
  .hero-section h1 { font-size: 2em; }
  .item-table { font-size: 0.85em; }
}
```

<div class="hero-section">
  <h1>Expert Content Review</h1>
  <p>
    Dear Researcher and Expert Reviewer,
    <br><br>
    Thank you for contributing your expertise to the ASQ-3 Saudi Arabic validation study.
    Your evaluation of each item is essential for ensuring that this developmental screening
    measure is culturally appropriate, linguistically sound, and psychometrically reliable
    for use in the Saudi Arabian context. Please rate each item on quality and clarity,
    then download your ratings as a CSV file and email it to the research team.
  </p>
</div>

<div id="successMessage" class="message-box success" style="display:none;"></div>
<div id="errorMessage" class="message-box error" style="display:none;"></div>

<div class="section-box">
  <h2 class="section-title">Reviewer Credentials</h2>
  <div class="section-description">
    Please provide your professional information. Fields marked with * are required.
  </div>
  <form id="expertForm">
    <div class="form-grid">
      <div class="form-group">
        <label>Full Name <span class="required">*</span></label>
        <input type="text" id="fullName" required>
      </div>
      <div class="form-group">
        <label>Email <span class="required">*</span></label>
        <input type="email" id="email" required>
      </div>
      <div class="form-group">
        <label>Institution/Organization</label>
        <input type="text" id="institution" placeholder="e.g., University Hospital, Research Center">
      </div>
      <div class="form-group">
        <label>Primary Field of Expertise <span class="required">*</span></label>
        <select id="expertise" required>
          <option value="">-- Select one --</option>
          <option value="child_development">Child Development / Developmental Psychology</option>
          <option value="pediatrics">Pediatrics / Pediatric Medicine</option>
          <option value="clinical_psychology">Clinical Psychology / Neuropsychology</option>
          <option value="speech_language">Speech-Language Pathology</option>
          <option value="special_education">Special Education</option>
          <option value="occupational_therapy">Occupational Therapy</option>
          <option value="education">Education / Early Childhood Education</option>
          <option value="other">Other</option>
        </select>
      </div>
      <div class="form-group">
        <label>Years of Professional Experience <span class="required">*</span></label>
        <input type="number" id="yearsExperience" min="0" placeholder="e.g., 15" required>
      </div>
      <div class="form-group">
        <label>Arabic Language Proficiency <span class="required">*</span></label>
        <select id="language" required>
          <option value="">-- Select level --</option>
          <option value="native">Native Speaker</option>
          <option value="fluent">Fluent / Proficient</option>
          <option value="intermediate">Intermediate</option>
          <option value="basic">Basic</option>
        </select>
      </div>
      <div class="form-group form-grid full">
        <label>Additional Professional Background (Optional)</label>
        <textarea id="additionalInfo" placeholder="Share relevant background, certifications, or research experience..."></textarea>
      </div>
    </div>
  </form>
</div>

<div class="section-box">
  <h2 class="section-title">Item Evaluation</h2>
  <div class="section-description">
    For each item below, rate <strong>Quality</strong> (how well it measures its intended developmental domain)
    and <strong>Clarity</strong> (how easily parents will understand the item).
    Scale: 1 = Poor/Unclear &nbsp;|&nbsp; 3 = Adequate &nbsp;|&nbsp; 5 = Excellent/Very Clear.
    Add comments as needed.
  </div>

```{r table, results='asis'}
cat('<div class="table-wrapper">\n')
cat('<table class="item-table">\n')
cat('  <thead>\n    <tr>\n')
cat('      <th style="width:6%">Month</th>\n')
cat('      <th style="width:12%">Domain</th>\n')
cat('      <th style="width:6%">Code</th>\n')
cat('      <th style="width:22%">Arabic Item</th>\n')
cat('      <th style="width:22%">English Item</th>\n')
cat('      <th style="width:10%;text-align:center">Quality<br>(1–5)</th>\n')
cat('      <th style="width:10%;text-align:center">Clarity<br>(1–5)</th>\n')
cat('      <th style="width:12%">Comments</th>\n')
cat('    </tr>\n  </thead>\n  <tbody>\n')

for (i in seq_len(nrow(items))) {
  row <- items[i, ]
  ar  <- if (is.na(row$item_text_ar)) "" else htmltools::htmlEscape(row$item_text_ar)
  en  <- if (is.na(row$item_text_en)) "" else htmltools::htmlEscape(row$item_text_en)
  cat(sprintf('    <tr>\n'))
  cat(sprintf('      <td>%s</td>\n', row$quest_label))
  cat(sprintf('      <td>%s</td>\n', row$domain))
  cat(sprintf('      <td><strong>%s</strong></td>\n', row$item_code))
  cat(sprintf('      <td dir="rtl" lang="ar">%s</td>\n', ar))
  cat(sprintf('      <td>%s</td>\n', en))
  cat(sprintf('      <td style="text-align:center"><select class="rating-select" id="quality_%d" data-item="%d" data-quest="%s" data-code="%s">\n', i, i, row$quest_label, row$item_code))
  cat('        <option value="">--</option>\n')
  for (r in 1:5) cat(sprintf('        <option value="%d">%d</option>\n', r, r))
  cat('      </select></td>\n')
  cat(sprintf('      <td style="text-align:center"><select class="rating-select" id="clarity_%d" data-item="%d">\n', i, i))
  cat('        <option value="">--</option>\n')
  for (r in 1:5) cat(sprintf('        <option value="%d">%d</option>\n', r, r))
  cat('      </select></td>\n')
  cat(sprintf('      <td><textarea class="comment-textarea" id="comment_%d"></textarea></td>\n', i))
  cat('    </tr>\n')
}

cat('  </tbody>\n</table>\n</div>\n')
```

</div>

<div class="button-container">
  <button type="button" class="btn btn-secondary" onclick="resetForm()">Clear All</button>
  <button type="button" class="btn btn-download" onclick="downloadCSV()">Download My Ratings (CSV)</button>
</div>

<p style="text-align:center;margin-top:20px;color:#666;font-size:0.9em;">
  After downloading, please email your CSV file to the research team.
</p>

<script>
function validateExpertForm() {
  const fullName = document.getElementById('fullName').value.trim();
  const email = document.getElementById('email').value.trim();
  const expertise = document.getElementById('expertise').value;
  const yearsExperience = document.getElementById('yearsExperience').value;
  const language = document.getElementById('language').value;
  const emailRegex = /^[^\s@]+@[^\s@]+\.[^\s@]+$/;
  if (!fullName) { showError('Full Name is required.'); return false; }
  if (!email || !emailRegex.test(email)) { showError('A valid Email is required.'); return false; }
  if (!expertise) { showError('Primary Field of Expertise is required.'); return false; }
  if (yearsExperience === '' || isNaN(yearsExperience)) { showError('Years of Professional Experience is required.'); return false; }
  if (!language) { showError('Arabic Language Proficiency is required.'); return false; }
  return true;
}

function showError(msg) {
  const el = document.getElementById('errorMessage');
  el.innerHTML = msg; el.style.display = 'block';
  document.getElementById('successMessage').style.display = 'none';
  window.scrollTo(0, 0);
}

function showSuccess(msg) {
  const el = document.getElementById('successMessage');
  el.innerHTML = msg; el.style.display = 'block';
  document.getElementById('errorMessage').style.display = 'none';
  window.scrollTo(0, 0);
}

function downloadCSV() {
  if (!validateExpertForm()) return;

  const expert = {
    fullName: document.getElementById('fullName').value.trim(),
    email: document.getElementById('email').value.trim(),
    institution: document.getElementById('institution').value.trim(),
    expertise: document.getElementById('expertise').value,
    yearsExperience: document.getElementById('yearsExperience').value,
    language: document.getElementById('language').value,
    additionalInfo: document.getElementById('additionalInfo').value.trim()
  };

  const rows = [['reviewer_name','reviewer_email','institution','expertise','years_experience','language','quest_label','item_code','quality','clarity','comments']];

  document.querySelectorAll('.item-table tbody tr').forEach((tr, idx) => {
    const n = idx + 1;
    const qSel = document.getElementById('quality_' + n);
    const cSel = document.getElementById('clarity_' + n);
    const comm = document.getElementById('comment_' + n);
    const questLabel = qSel ? qSel.getAttribute('data-quest') : '';
    const itemCode  = qSel ? qSel.getAttribute('data-code')  : '';
    rows.push([
      csvEscape(expert.fullName),
      csvEscape(expert.email),
      csvEscape(expert.institution),
      csvEscape(expert.expertise),
      csvEscape(expert.yearsExperience),
      csvEscape(expert.language),
      csvEscape(questLabel),
      csvEscape(itemCode),
      qSel ? qSel.value : '',
      cSel ? cSel.value : '',
      comm ? csvEscape(comm.value.trim()) : ''
    ]);
  });

  const csvContent = rows.map(r => r.join(',')).join('\n');
  const blob = new Blob(['\uFEFF' + csvContent], { type: 'text/csv;charset=utf-8;' });
  const url = URL.createObjectURL(blob);
  const a = document.createElement('a');
  a.href = url;
  a.download = 'asq3_review_' + expert.fullName.replace(/\s+/g, '_') + '.csv';
  document.body.appendChild(a);
  a.click();
  document.body.removeChild(a);
  URL.revokeObjectURL(url);
  showSuccess('Your ratings have been downloaded. Please email the CSV file to the research team. Thank you, ' + expert.fullName + '!');
}

function csvEscape(val) {
  if (val === null || val === undefined) return '';
  const s = String(val);
  if (s.includes(',') || s.includes('"') || s.includes('\n')) {
    return '"' + s.replace(/"/g, '""') + '"';
  }
  return s;
}

function resetForm() {
  document.getElementById('expertForm').reset();
  document.querySelectorAll('.rating-select').forEach(el => el.value = '');
  document.querySelectorAll('.comment-textarea').forEach(el => el.value = '');
  document.getElementById('errorMessage').style.display = 'none';
  document.getElementById('successMessage').style.display = 'none';
}
</script>
