---
title: "Content Review"
format: 
  html:
    toc: false
---

```{r setup, include=FALSE}
source("R/data_setup.R")
```

```{css}
:root {
  --primary-green: #1DB584;
  --secondary-blue: #4A90E2;
  --accent-purple: #7B68EE;
  --light-gray: #F5F5F5;
  --dark-text: #333333;
  --border-gray: #CCCCCC;
}

* {
  margin: 0;
  padding: 0;
  box-sizing: border-box;
}

html, body {
  font-family: -apple-system, BlinkMacSystemFont, 'Segoe UI', Roboto, Helvetica, Arial, sans-serif;
  background-color: var(--light-gray);
  color: var(--dark-text);
  line-height: 1.6;
}

.hero-section {
  background: linear-gradient(135deg, var(--primary-green) 0%, var(--secondary-blue) 100%);
  color: white;
  padding: 60px 40px;
  text-align: center;
  margin-bottom: 50px;
}

.hero-section h1 {
  font-size: 2.5em;
  margin-bottom: 20px;
  font-weight: 700;
  letter-spacing: 0.5px;
}

.hero-section p {
  font-size: 1.1em;
  max-width: 800px;
  margin: 0 auto;
  line-height: 1.8;
  opacity: 0.98;
}

.message-box {
  padding: 15px 20px;
  margin-bottom: 30px;
  border-radius: 4px;
  border-left: 5px solid var(--primary-green);
  background-color: #EAFAF3;
  color: #1a6643;
  display: none;
}

.message-box.success {
  border-left-color: var(--primary-green);
  background-color: #EAFAF3;
  color: #1a6643;
  display: block;
}

.message-box.error {
  border-left-color: #DC3545;
  background-color: #F8D7DA;
  color: #721C24;
  display: block;
}

.section-box {
  background: white;
  margin-bottom: 40px;
  border-radius: 6px;
  box-shadow: 0 2px 8px rgba(0,0,0,0.1);
  padding: 40px;
}

.section-title {
  font-size: 1.8em;
  font-weight: 700;
  color: var(--primary-green);
  margin-bottom: 10px;
  padding-bottom: 15px;
  border-bottom: 3px solid var(--secondary-blue);
}

.section-description {
  color: #666;
  font-size: 0.95em;
  margin-bottom: 30px;
  padding: 15px;
  background-color: var(--light-gray);
  border-radius: 4px;
  border-left: 4px solid var(--secondary-blue);
}

.form-grid {
  display: grid;
  grid-template-columns: 1fr 1fr;
  gap: 25px;
  margin-bottom: 30px;
}

.form-grid.full {
  grid-template-columns: 1fr;
}

.form-group {
  display: flex;
  flex-direction: column;
}

.form-group label {
  font-weight: 600;
  margin-bottom: 8px;
  font-size: 0.95em;
  color: var(--dark-text);
}

.form-group label .required {
  color: #DC3545;
  margin-left: 3px;
}

.form-group input,
.form-group select,
.form-group textarea {
  padding: 12px 14px;
  border: 2px solid var(--border-gray);
  border-radius: 4px;
  font-size: 1em;
  font-family: inherit;
  background-color: white;
  color: var(--dark-text);
  transition: all 0.3s ease;
}

.form-group input:focus,
.form-group select:focus,
.form-group textarea:focus {
  outline: none;
  border-color: var(--primary-green);
  box-shadow: 0 0 8px rgba(29, 181, 132, 0.2);
}

.form-group textarea {
  resize: vertical;
  min-height: 80px;
}

.table-wrapper {
  overflow-x: auto;
  margin-top: 30px;
}

.item-table {
  width: 100%;
  border-collapse: collapse;
  font-size: 0.95em;
}

.item-table thead {
  background-color: var(--primary-green);
  color: white;
  position: sticky;
  top: 0;
  z-index: 10;
}

.item-table thead th {
  padding: 15px 12px;
  text-align: left;
  font-weight: 600;
  border: 1px solid #999;
}

.item-table tbody tr {
  border-bottom: 1px solid #ddd;
}

.item-table tbody tr:nth-child(even) {
  background-color: #FAFAFA;
}

.item-table tbody tr:hover {
  background-color: #F0F8F5;
}

.item-table td {
  padding: 12px;
  border: 1px solid #ddd;
}

.item-table .rating-select {
  width: 70px;
  padding: 8px;
  border: 1px solid var(--border-gray);
  border-radius: 3px;
  font-size: 0.9em;
}

.item-table .comment-textarea {
  width: 100%;
  padding: 8px;
  border: 1px solid var(--border-gray);
  border-radius: 3px;
  font-size: 0.85em;
  min-height: 60px;
  font-family: inherit;
  resize: vertical;
}

.button-container {
  display: flex;
  gap: 15px;
  justify-content: center;
  margin-top: 50px;
  flex-wrap: wrap;
}

.btn {
  padding: 14px 40px;
  border: none;
  border-radius: 4px;
  font-size: 1em;
  font-weight: 600;
  cursor: pointer;
  text-transform: uppercase;
  letter-spacing: 0.5px;
  transition: all 0.3s ease;
}

.btn-primary {
  background-color: var(--primary-green);
  color: white;
}

.btn-primary:hover {
  background-color: #169D6E;
  transform: translateY(-2px);
  box-shadow: 0 4px 12px rgba(29, 181, 132, 0.3);
}

.btn-secondary {
  background-color: var(--secondary-blue);
  color: white;
}

.btn-secondary:hover {
  background-color: #3A7BC8;
  transform: translateY(-2px);
  box-shadow: 0 4px 12px rgba(74, 144, 226, 0.3);
}

.loading {
  display: none;
  text-align: center;
  padding: 20px;
}

.spinner {
  border: 4px solid var(--light-gray);
  border-top: 4px solid var(--primary-green);
  border-radius: 50%;
  width: 40px;
  height: 40px;
  animation: spin 1s linear infinite;
  margin: 0 auto 15px;
}

@keyframes spin {
  0% { transform: rotate(0deg); }
  100% { transform: rotate(360deg); }
}

@media (max-width: 768px) {
  .form-grid {
    grid-template-columns: 1fr;
  }
  
  .section-box {
    padding: 20px;
  }
  
  .hero-section {
    padding: 40px 20px;
  }
  
  .hero-section h1 {
    font-size: 2em;
  }
  
  .item-table {
    font-size: 0.85em;
  }
  
  .item-table td {
    padding: 8px;
  }
  
  .item-table .rating-select,
  .item-table .comment-textarea {
    font-size: 0.8em;
  }
}
```

<div class="hero-section">
  <h1>Expert Content Review</h1>
  <p>
    Dear Researcher and Expert Reviewer,
    <br><br>
    Thank you for contributing your expertise to the ASQ-3 Saudi Arabic validation study. 
    Your rigorous evaluation of each item is essential for ensuring that this developmental screening 
    measure is culturally appropriate, linguistically sound, and psychometrically reliable for use in 
    the Saudi Arabian context. Please complete the form below by rating each item on quality and clarity, 
    and providing any clinical observations that may be relevant for implementation.
  </p>
</div>

<div id="successMessage" class="message-box success"></div>
<div id="errorMessage" class="message-box error"></div>

<div class="section-box">
  <h2 class="section-title">Reviewer Credentials</h2>
  
  <div class="section-description">
    Please provide your professional information. This allows us to contextually analyze 
    expert feedback by specialization and experience level (fields marked with * are required).
  </div>
  
  <form id="expertForm">
    <div class="form-grid">
      <div class="form-group">
        <label>Full Name <span class="required">*</span></label>
        <input type="text" id="fullName" name="fullName" required>
      </div>
      
      <div class="form-group">
        <label>Email <span class="required">*</span></label>
        <input type="email" id="email" name="email" required>
      </div>
      
      <div class="form-group">
        <label>Institution/Organization</label>
        <input type="text" id="institution" name="institution" placeholder="e.g., University Hospital, Research Center">
      </div>
      
      <div class="form-group">
        <label>Primary Field of Expertise <span class="required">*</span></label>
        <select id="expertise" name="expertise" required>
          <option value="">-- Select one --</option>
          <option value="child_development">Child Development/Developmental Psychology</option>
          <option value="pediatrics">Pediatrics/Pediatric Medicine</option>
          <option value="clinical_psychology">Clinical Psychology/Neuropsychology</option>
          <option value="speech_language">Speech-Language Pathology</option>
          <option value="special_education">Special Education</option>
          <option value="occupational_therapy">Occupational Therapy</option>
          <option value="education">Education/Early Childhood Education</option>
          <option value="other">Other</option>
        </select>
      </div>
      
      <div class="form-group">
        <label>Years of Professional Experience <span class="required">*</span></label>
        <input type="number" id="yearsExperience" name="yearsExperience" min="0" placeholder="e.g., 15" required>
      </div>
      
      <div class="form-group">
        <label>Arabic Language Proficiency <span class="required">*</span></label>
        <select id="language" name="language" required>
          <option value="">-- Select level --</option>
          <option value="native">Native Speaker</option>
          <option value="fluent">Fluent/Proficient</option>
          <option value="intermediate">Intermediate</option>
          <option value="basic">Basic</option>
        </select>
      </div>
      
      <div class="form-group form-grid full">
        <label>Additional Professional Background (Optional)</label>
        <textarea id="additionalInfo" name="additionalInfo" placeholder="Share relevant background, certifications, or research experience..."></textarea>
      </div>
    </div>
  </form>
</div>

<div class="section-box">
  <h2 class="section-title">Item Evaluation</h2>
  
  <div class="section-description">
    For each of the 630 ASQ-3 items below, please rate the item's quality (how well it measures its intended developmental domain) 
    and clarity (how easily parents will understand the item). Use the scale: 1 = Poor/Unclear, 3 = Adequate, 5 = Excellent/Very Clear. 
    Add comments as needed to support your ratings or flag concerns.
  </div>

```{r}
#| results: asis

# Prepare data
if (exists("item_dictionary_with_stats") && nrow(item_dictionary_with_stats) > 0) {
  eval_data <- item_dictionary_with_stats %>%
    select(quest, domain, item_code, item_text_ar, item_text_en) %>%
    rename(
      questionnaire = quest,
      arabic = item_text_ar,
      english = item_text_en
    )
} else {
  eval_data <- tibble(
    questionnaire = integer(),
    domain = character(),
    item_code = character(),
    arabic = character(),
    english = character()
  )
}

# Start table
cat('<div class="table-wrapper">\n')
cat('<table class="item-table">\n')
cat('  <thead>\n')
cat('    <tr>\n')
cat('      <th style="width: 6%;">Month</th>\n')
cat('      <th style="width: 12%;">Domain</th>\n')
cat('      <th style="width: 6%;">Code</th>\n')
cat('      <th style="width: 22%;">Arabic Item</th>\n')
cat('      <th style="width: 22%;">English Item</th>\n')
cat('      <th style="width: 10%; text-align: center;">Quality (1-5)</th>\n')
cat('      <th style="width: 10%; text-align: center;">Clarity (1-5)</th>\n')
cat('      <th style="width: 12%;">Comments</th>\n')
cat('    </tr>\n')
cat('  </thead>\n')
cat('  <tbody>\n')

# Add rows
for (i in seq_len(nrow(eval_data))) {
  row <- eval_data[i, ]
  
  cat(sprintf('    <tr>\n'))
  cat(sprintf('      <td>%s</td>\n', row$questionnaire))
  cat(sprintf('      <td>%s</td>\n', row$domain))
  cat(sprintf('      <td><strong>%s</strong></td>\n', row$item_code))
  cat(sprintf('      <td>%s</td>\n', substr(row$arabic, 1, 80)))
  cat(sprintf('      <td>%s</td>\n', substr(row$english, 1, 80)))
  cat(sprintf('      <td style="text-align: center;"><select class="rating-select" id="quality_%d" data-item="%d">\n', i, i))
  cat('        <option value="">--</option>\n')
  for (rating in 1:5) {
    cat(sprintf('        <option value="%d">%d</option>\n', rating, rating))
  }
  cat('      </select></td>\n')
  cat(sprintf('      <td style="text-align: center;"><select class="rating-select" id="clarity_%d" data-item="%d">\n', i, i))
  cat('        <option value="">--</option>\n')
  for (rating in 1:5) {
    cat(sprintf('        <option value="%d">%d</option>\n', rating, rating))
  }
  cat('      </select></td>\n')
  cat(sprintf('      <td><textarea class="comment-textarea" id="comment_%d"></textarea></td>\n', i))
  cat('    </tr>\n')
}

# Close table
cat('  </tbody>\n')
cat('</table>\n')
cat('</div>\n')
```

</div>

<div class="button-container">
  <button type="button" class="btn btn-secondary" onclick="resetForm()">Clear All</button>
  <button type="button" class="btn btn-primary" onclick="submitEvaluation()">Submit Review</button>
</div>

<div class="loading" id="loadingIndicator">
  <div class="spinner"></div>
  <p>Processing your submission...</p>
</div>

<script>
function validateExpertForm() {
  const fullName = document.getElementById('fullName').value.trim();
  const email = document.getElementById('email').value.trim();
  const expertise = document.getElementById('expertise').value;
  const yearsExperience = document.getElementById('yearsExperience').value;
  const language = document.getElementById('language').value;
  
  if (!fullName) {
    showError('Full Name is required.');
    return false;
  }
  
  if (!email) {
    showError('Email is required.');
    return false;
  }
  
  const emailRegex = /^[^\s@]+@[^\s@]+\.[^\s@]+$/;
  if (!emailRegex.test(email)) {
    showError('Please enter a valid email address.');
    return false;
  }
  
  if (!expertise) {
    showError('Primary Field of Expertise is required.');
    return false;
  }
  
  if (yearsExperience === '' || isNaN(yearsExperience)) {
    showError('Years of Professional Experience is required.');
    return false;
  }
  
  if (!language) {
    showError('Arabic Language Proficiency is required.');
    return false;
  }
  
  return true;
}

function collectEvaluationData() {
  const data = {
    expert: {
      fullName: document.getElementById('fullName').value.trim(),
      email: document.getElementById('email').value.trim(),
      institution: document.getElementById('institution').value.trim(),
      expertise: document.getElementById('expertise').value,
      yearsExperience: parseInt(document.getElementById('yearsExperience').value),
      language: document.getElementById('language').value,
      additionalInfo: document.getElementById('additionalInfo').value.trim()
    },
    evaluations: []
  };
  
  const tableRows = document.querySelectorAll('.item-table tbody tr');
  
  tableRows.forEach((row, index) => {
    const itemNum = index + 1;
    const qualitySelect = document.getElementById(`quality_${itemNum}`);
    const claritySelect = document.getElementById(`clarity_${itemNum}`);
    const commentTextarea = document.getElementById(`comment_${itemNum}`);
    
    data.evaluations.push({
      itemIndex: itemNum,
      quality: qualitySelect ? qualitySelect.value : null,
      clarity: claritySelect ? claritySelect.value : null,
      comment: commentTextarea ? commentTextarea.value.trim() : ''
    });
  });
  
  return data;
}

function showError(message) {
  const errorBox = document.getElementById('errorMessage');
  errorBox.innerHTML = message;
  errorBox.style.display = 'block';
  document.getElementById('successMessage').style.display = 'none';
  window.scrollTo(0, 0);
}

function showSuccess(message) {
  const successBox = document.getElementById('successMessage');
  successBox.innerHTML = message;
  successBox.style.display = 'block';
  document.getElementById('errorMessage').style.display = 'none';
  window.scrollTo(0, 0);
}

async function submitEvaluation() {
  document.getElementById('errorMessage').style.display = 'none';
  document.getElementById('successMessage').style.display = 'none';
  
  if (!validateExpertForm()) {
    return;
  }
  
  const evaluationData = collectEvaluationData();
  document.getElementById('loadingIndicator').style.display = 'block';
  
  try {
    const response = await fetch('/.netlify/functions/save-evaluation', {
      method: 'POST',
      headers: {
        'Content-Type': 'application/json',
      },
      body: JSON.stringify(evaluationData)
    });
    
    document.getElementById('loadingIndicator').style.display = 'none';
    
    if (response.ok) {
      showSuccess(`Thank you, Dr./Prof. ${evaluationData.expert.fullName}. Your expert review has been successfully recorded in our database.`);
      setTimeout(() => {
        resetForm();
      }, 3000);
    } else {
      const errorDetails = await response.json().catch(() => ({}));
      showError(errorDetails.message || 'Error recording your submission. Please try again.');
    }
  } catch (error) {
    document.getElementById('loadingIndicator').style.display = 'none';
    console.error('Submission error:', error);
    
    try {
      const timestamp = new Date().toISOString();
      const savedEvaluations = JSON.parse(localStorage.getItem('asq3_evaluations') || '[]');
      savedEvaluations.push({
        timestamp: timestamp,
        ...evaluationData
      });
      localStorage.setItem('asq3_evaluations', JSON.stringify(savedEvaluations));
      showSuccess(`Thank you, Dr./Prof. ${evaluationData.expert.fullName}. Your review has been saved locally (${savedEvaluations.length} total review(s) recorded).`);
      setTimeout(() => {
        resetForm();
      }, 3000);
    } catch (localError) {
      showError('Error saving your submission. Please check your connection and try again.');
    }
  }
}

function resetForm() {
  document.getElementById('expertForm').reset();
  document.querySelectorAll('.rating-select').forEach(el => el.value = '');
  document.querySelectorAll('.comment-textarea').forEach(el => el.value = '');
  document.getElementById('errorMessage').style.display = 'none';
  document.getElementById('successMessage').style.display = 'none';
}
</script>
```
