---
title: "Content Review"
format: html
---

```{r}
source("R/data_setup.R")
```

```{css}
:root {
  --primary-color: #1F6AA5;
  --secondary-color: #2E8B9E;
  --accent-color: #F39C12;
  --success-color: #27AE60;
  --danger-color: #E74C3C;
  --light-gray: #ECF0F1;
  --dark-gray: #34495E;
}

body {
  font-family: 'Segoe UI', Tahoma, Geneva, Verdana, sans-serif;
  background-color: #F8F9FA;
  color: var(--dark-gray);
}

.hero-section {
  background: linear-gradient(135deg, var(--primary-color) 0%, var(--secondary-color) 100%);
  color: white;
  padding: 50px 30px;
  border-radius: 10px;
  margin-bottom: 40px;
  box-shadow: 0 4px 15px rgba(0,0,0,0.1);
}

.hero-section h1 {
  margin: 0 0 15px 0;
  font-size: 2.5em;
  font-weight: 700;
}

.hero-section p {
  margin: 0;
  font-size: 1.1em;
  opacity: 0.95;
  line-height: 1.6;
}

.form-section {
  background: white;
  padding: 40px;
  border-radius: 8px;
  box-shadow: 0 2px 8px rgba(0,0,0,0.08);
  margin-bottom: 40px;
}

.form-section h2 {
  color: var(--primary-color);
  border-bottom: 3px solid var(--accent-color);
  padding-bottom: 15px;
  margin-bottom: 30px;
  font-size: 1.8em;
}

.form-grid {
  display: grid;
  grid-template-columns: 1fr 1fr;
  gap: 20px;
  margin-bottom: 25px;
}

.form-group {
  display: flex;
  flex-direction: column;
}

.form-group label {
  font-weight: 600;
  color: var(--dark-gray);
  margin-bottom: 8px;
  font-size: 0.95em;
}

.form-group input,
.form-group select,
.form-group textarea {
  padding: 12px;
  border: 2px solid var(--light-gray);
  border-radius: 5px;
  font-size: 1em;
  font-family: inherit;
  transition: border-color 0.3s ease;
}

.form-group input:focus,
.form-group select:focus,
.form-group textarea:focus {
  outline: none;
  border-color: var(--primary-color);
  box-shadow: 0 0 5px rgba(31, 106, 165, 0.2);
}

.form-group.full {
  grid-column: 1 / -1;
}

.alert-info {
  background-color: #E3F2FD;
  border-left: 4px solid var(--primary-color);
  padding: 15px;
  border-radius: 4px;
  margin-bottom: 30px;
  color: #1565C0;
}

.table-section {
  background: white;
  padding: 40px;
  border-radius: 8px;
  box-shadow: 0 2px 8px rgba(0,0,0,0.08);
  margin-bottom: 40px;
}

.table-section h2 {
  color: var(--primary-color);
  border-bottom: 3px solid var(--accent-color);
  padding-bottom: 15px;
  margin-bottom: 30px;
  font-size: 1.8em;
}

.item-table-container {
  overflow-x: auto;
  margin: 20px 0;
}

.item-table {
  width: 100%;
  border-collapse: collapse;
  font-size: 0.95em;
}

.item-table thead {
  background-color: var(--primary-color);
  color: white;
  position: sticky;
  top: 0;
}

.item-table thead th {
  padding: 15px;
  text-align: left;
  border: 1px solid #ddd;
  font-weight: 600;
}

.item-table tbody tr:nth-child(even) {
  background-color: #F8F9FA;
}

.item-table tbody tr:hover {
  background-color: #E8F4F8;
}

.item-table td {
  padding: 12px 15px;
  border: 1px solid #ddd;
}

.quality-rating, .clarity-rating {
  width: 60px;
  padding: 8px;
  border: 1px solid var(--light-gray);
  border-radius: 4px;
  font-size: 0.95em;
}

.comment-input {
  width: 100%;
  padding: 8px;
  border: 1px solid var(--light-gray);
  border-radius: 4px;
  font-size: 0.9em;
  font-family: 'Segoe UI', Tahoma, Geneva, Verdana, sans-serif;
  resize: vertical;
  min-width: 150px;
}

.button-group {
  display: flex;
  gap: 15px;
  margin-top: 40px;
  justify-content: center;
  flex-wrap: wrap;
}

.btn {
  padding: 14px 35px;
  border: none;
  border-radius: 5px;
  font-size: 1em;
  font-weight: 600;
  cursor: pointer;
  transition: all 0.3s ease;
  text-transform: uppercase;
  letter-spacing: 0.5px;
}

.btn-primary {
  background-color: var(--primary-color);
  color: white;
  box-shadow: 0 4px 10px rgba(31, 106, 165, 0.3);
}

.btn-primary:hover {
  background-color: #165080;
  transform: translateY(-2px);
  box-shadow: 0 6px 15px rgba(31, 106, 165, 0.4);
}

.btn-secondary {
  background-color: var(--light-gray);
  color: var(--dark-gray);
  box-shadow: 0 2px 5px rgba(0,0,0,0.1);
}

.btn-secondary:hover {
  background-color: #D5DBDB;
  transform: translateY(-2px);
}

.success-message {
  background-color: #D5F4E6;
  border-left: 4px solid var(--success-color);
  padding: 15px;
  border-radius: 4px;
  color: #186A3B;
  margin-bottom: 20px;
  display: none;
  animation: slideIn 0.3s ease;
}

.error-message {
  background-color: #FADBD8;
  border-left: 4px solid var(--danger-color);
  padding: 15px;
  border-radius: 4px;
  color: #A93226;
  margin-bottom: 20px;
  display: none;
  animation: slideIn 0.3s ease;
}

@keyframes slideIn {
  from {
    opacity: 0;
    transform: translateY(-10px);
  }
  to {
    opacity: 1;
    transform: translateY(0);
  }
}

.loading {
  display: none;
  text-align: center;
  padding: 20px;
}

.spinner {
  border: 4px solid var(--light-gray);
  border-top: 4px solid var(--primary-color);
  border-radius: 50%;
  width: 40px;
  height: 40px;
  animation: spin 1s linear infinite;
  margin: 0 auto;
}

@keyframes spin {
  0% { transform: rotate(0deg); }
  100% { transform: rotate(360deg); }
}
```

<div class="hero-section">
  <h1>📋 Expert Content Review</h1>
  <p>
    Thank you for participating in the ASQ-3 Saudi Arabic validation study. 
    Please fill out your expert information below and then evaluate each item 
    based on its quality to measure the intended domain and clarity for parents. 
    Your feedback is invaluable for ensuring this assessment is culturally appropriate 
    and psychometrically sound.
  </p>
</div>

<div id="successMessage" class="success-message">
  ✓ Thank you! Your responses have been saved successfully.
</div>

<div id="errorMessage" class="error-message">
  ✗ There was an error saving your responses. Please try again.
</div>

<div class="loading" id="loadingIndicator">
  <div class="spinner"></div>
  <p>Saving your responses...</p>
</div>

<div class="form-section">
  <h2>Expert Information</h2>
  
  <div class="alert-info">
    <strong>ℹ️ Note:</strong> Please provide your credentials and expertise area. 
    This information helps us contextualize your feedback. Fields marked with * are required.
  </div>
  
  <form id="expertForm">
    <div class="form-grid">
      <div class="form-group">
        <label for="fullName">Full Name *</label>
        <input type="text" id="fullName" name="fullName" required>
      </div>
      
      <div class="form-group">
        <label for="email">Email *</label>
        <input type="email" id="email" name="email" required>
      </div>
      
      <div class="form-group">
        <label for="institution">Institution/Organization</label>
        <input type="text" id="institution" name="institution">
      </div>
      
      <div class="form-group">
        <label for="expertise">Area of Expertise *</label>
        <select id="expertise" name="expertise" required>
          <option value="">-- Select an area --</option>
          <option value="child_development">Child Development</option>
          <option value="pediatrics">Pediatrics</option>
          <option value="psychology">Psychology/Assessment</option>
          <option value="speech_language">Speech-Language Pathology</option>
          <option value="special_education">Special Education</option>
          <option value="occupational_therapy">Occupational Therapy</option>
          <option value="other">Other</option>
        </select>
      </div>
      
      <div class="form-group">
        <label for="yearsExperience">Years of Experience in Field *</label>
        <input type="number" id="yearsExperience" name="yearsExperience" min="0" required>
      </div>
      
      <div class="form-group">
        <label for="language">Arabic Language Proficiency *</label>
        <select id="language" name="language" required>
          <option value="">-- Select level --</option>
          <option value="native">Native Speaker</option>
          <option value="fluent">Fluent</option>
          <option value="proficient">Proficient</option>
          <option value="intermediate">Intermediate</option>
        </select>
      </div>
      
      <div class="form-group full">
        <label for="additionalInfo">Additional Comments (Optional)</label>
        <textarea id="additionalInfo" name="additionalInfo" rows="4" placeholder="Share any relevant background information..."></textarea>
      </div>
    </div>
  </form>
</div>

<div class="table-section">
  <h2>Item Evaluation</h2>
  
  <div class="alert-info">
    <strong>ℹ️ Instructions:</strong> For each item below, rate its quality and clarity 
    (1 = Poor/Not Clear, 5 = Excellent/Very Clear) and add any comments you deem necessary.
  </div>

```{r}
#| results: asis

# Create evaluation table with ratings and comments
item_bank_data <- item_dictionary_with_stats %>%
  select(quest, domain, item_code, item_text_ar, item_text_en) %>%
  rename(
    questionnaire = quest,
    arabic = item_text_ar,
    english = item_text_en
  )

cat('
<div class="item-table-container">
<table class="item-table" id="evaluationTable">
  <thead>
    <tr>
      <th style="width: 8%;">Quest</th>
      <th style="width: 10%;">Domain</th>
      <th style="width: 8%;">Code</th>
      <th style="width: 20%;">Arabic Item</th>
      <th style="width: 20%;">English Item</th>
      <th style="width: 8%; text-align: center;">Quality<br/>(1-5)</th>
      <th style="width: 8%; text-align: center;">Clarity<br/>(1-5)</th>
      <th style="width: 18%;">Comments</th>
    </tr>
  </thead>
  <tbody>
')

for (i in seq_len(nrow(item_bank_data))) {
  row <- item_bank_data[i, ]
  quality_id <- paste0("quality_", i)
  clarity_id <- paste0("clarity_", i)
  comment_id <- paste0("comment_", i)
  
  cat(sprintf('
    <tr>
      <td>%s</td>
      <td>%s</td>
      <td><strong>%s</strong></td>
      <td>%s</td>
      <td>%s</td>
      <td style="text-align: center;">
        <select id="%s" class="quality-rating" data-item="%d">
          <option value="">--</option>
          <option value="1">1</option>
          <option value="2">2</option>
          <option value="3">3</option>
          <option value="4">4</option>
          <option value="5">5</option>
        </select>
      </td>
      <td style="text-align: center;">
        <select id="%s" class="clarity-rating" data-item="%d">
          <option value="">--</option>
          <option value="1">1</option>
          <option value="2">2</option>
          <option value="3">3</option>
          <option value="4">4</option>
          <option value="5">5</option>
        </select>
      </td>
      <td>
        <textarea id="%s" class="comment-input" placeholder="Add comments..."></textarea>
      </td>
    </tr>
  ', row$questionnaire, row$domain, row$item_code, 
    substr(row$arabic, 1, 60), substr(row$english, 1, 60),
    quality_id, i, clarity_id, i, comment_id))
}

cat('
  </tbody>
</table>
</div>
')
```

</div>

<div class="button-group">
  <button type="button" class="btn btn-secondary" onclick="resetForm()">Clear All</button>
  <button type="button" class="btn btn-primary" onclick="submitEvaluation()">Submit Review</button>
</div>

```{javascript}
function validateExpertForm() {
  const fullName = document.getElementById('fullName').value.trim();
  const email = document.getElementById('email').value.trim();
  const expertise = document.getElementById('expertise').value;
  const yearsExperience = document.getElementById('yearsExperience').value;
  const language = document.getElementById('language').value;
  
  if (!fullName || !email || !expertise || yearsExperience === '' || !language) {
    showError('Please fill out all required expert information fields.');
    return false;
  }
  
  const emailRegex = /^[^\s@]+@[^\s@]+\.[^\s@]+$/;
  if (!emailRegex.test(email)) {
    showError('Please enter a valid email address.');
    return false;
  }
  
  return true;
}

function collectEvaluationData() {
  const data = {
    expert: {
      fullName: document.getElementById('fullName').value,
      email: document.getElementById('email').value,
      institution: document.getElementById('institution').value,
      expertise: document.getElementById('expertise').value,
      yearsExperience: document.getElementById('yearsExperience').value,
      language: document.getElementById('language').value,
      additionalInfo: document.getElementById('additionalInfo').value
    },
    evaluations: []
  };
  
  const qualityInputs = document.querySelectorAll('.quality-rating');
  
  qualityInputs.forEach((input) => {
    const itemIndex = input.dataset.item;
    const clarityInput = document.getElementById(`clarity_${itemIndex}`);
    const commentInput = document.getElementById(`comment_${itemIndex}`);
    
    data.evaluations.push({
      itemIndex: itemIndex,
      quality: input.value || null,
      clarity: clarityInput.value || null,
      comment: commentInput.value || ''
    });
  });
  
  return data;
}

function showError(message) {
  document.getElementById('errorMessage').innerHTML = '✗ ' + message;
  document.getElementById('errorMessage').style.display = 'block';
  document.getElementById('successMessage').style.display = 'none';
  window.scrollTo(0, 0);
}

function showSuccess(message) {
  document.getElementById('successMessage').innerHTML = '✓ ' + message;
  document.getElementById('successMessage').style.display = 'block';
  document.getElementById('errorMessage').style.display = 'none';
  window.scrollTo(0, 0);
}

async function submitEvaluation() {
  document.getElementById('errorMessage').style.display = 'none';
  document.getElementById('successMessage').style.display = 'none';
  
  if (!validateExpertForm()) {
    return;
  }
  
  const evaluationData = collectEvaluationData();
  
  document.getElementById('loadingIndicator').style.display = 'block';
  
  try {
    const response = await fetch('/.netlify/functions/save-evaluation', {
      method: 'POST',
      headers: {
        'Content-Type': 'application/json',
      },
      body: JSON.stringify(evaluationData)
    });
    
    document.getElementById('loadingIndicator').style.display = 'none';
    
    if (response.ok) {
      showSuccess(`Thank you ${evaluationData.expert.fullName}! Your review has been saved.`);
      setTimeout(() => {
        resetForm();
      }, 2000);
    } else {
      const error = await response.json();
      showError(error.message || 'Error saving your response. Please try again.');
    }
  } catch (error) {
    document.getElementById('loadingIndicator').style.display = 'none';
    console.error('Error:', error);
    
    // Fallback to localStorage if Netlify Functions fail
    try {
      const timestamp = new Date().toISOString();
      const savedEvaluations = JSON.parse(localStorage.getItem('asq3_evaluations') || '[]');
      savedEvaluations.push({
        timestamp: timestamp,
        ...evaluationData
      });
      localStorage.setItem('asq3_evaluations', JSON.stringify(savedEvaluations));
      showSuccess(`Thank you ${evaluationData.expert.fullName}! Your review has been saved locally (${savedEvaluations.length} total).`);
      setTimeout(() => {
        resetForm();
      }, 2000);
    } catch (fallbackError) {
      showError('Error saving your response. Please try again.');
    }
  }
}

function resetForm() {
  document.getElementById('expertForm').reset();
  document.querySelectorAll('.quality-rating, .clarity-rating').forEach(el => el.value = '');
  document.querySelectorAll('.comment-input').forEach(el => el.value = '');
  document.getElementById('errorMessage').style.display = 'none';
  document.getElementById('successMessage').style.display = 'none';
}
```
```
